Sparsity Weak Lensing $3$-D Density Map Reconstruction: Reducing the line of sight smearing.

### 2020-10-26 doc/paper_ms_method_HSCY1/ms.tex
some detailed modification

\begin{document}
\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction: 
Reducing the line-of-sight smearing.}
%\author{Xiangchong Li}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Masamune Oguri}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
%\author{Wentao Luo}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{HSC Collaboration}
%\noaffiliation
%\email{xiangchong.li@ipmu.jp}

\begin{abstract}
A new method is developed to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
The $3$-D density contrast maps are modeled as a summation of the NFW basis atoms which have $2$-D multi-scale NFW surface 
density profiles on the transverse plane and $1$-D Dirac delta functions in the line-of-sight direction. With the prior 
assumption that the density fields can be sparsely represented by the NFW basis atoms, it is reconstructed using an 
oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape noise and 
photo-$z$ uncertainty.
Our findings are summarized as folllows: 1) The global minima solution of the standard lasso algorithm suffers from a
smear of structure in the line-of-sight direction even in the absence of shape nosie.
2) The global minima solution of addaptive lasso algorithm significantly removes the line-of-sight smear of structure.
\end{abstract}

@@

Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line-of-sight
due to the influence of gravity. As a result of the light distortion, the shapes of the background galaxies are coherently
distorted. Such effect, which is known as weak lensing, imprints the information of foreground mass density distribution
to the background galaxy images and offers a direct probe into the mass density distribution in our universe
\citep[see][for recent reviews]{revKilbinger15,revRachel17}.

@@

Several large scale surveys target to study the weak lensing effect at high precision level (e.g. HSC \citep{HSC1-data}, KIDS
\citep{KIDS13}, DES \citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, WFIRST \citep{WFIRST15}).

The primary goal of most weak lensing surveys is to constrain the cosmology model through $2$-point correlations. The studies
include galaxy-galaxy lensing which cross correlating the shear field ($\gamma$) with the positions of foreground galaxies
\citep{gglens-GAMA-Han2014,gglens-BossCFHTMore2015,gglens-DES1},
and cosmic shear which auto-correlates the shear measurements
\citep{cosmicShearRealKids450,cosmicShear-DES1,cosmicShear_HSC1_Chiaki2019,cosmicShear_HSC1_Hamana2019}.
Since shear is directly related to the matter distribution as shown in eq. (\ref{eq-intro-delta2shear}), Galaxy-galaxy lensing
probes into the correlation between the matter field and galaxy field, on the other hand, cosmic shear probes into the
auto-correlation of matter field.

The reconstruction of density map from shear measurements also receive considerable interest as it reaches the nonlinear scales. 
$2$-D density map reconstruction which recover an integration of projected mass along the line-of-sight has been well studied 
within the community \citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However, the 
reconstruction of $3$-D mass map is still a challenging task.

@@

\citet{LSS-massMap-Wiener-Simon2009} propose to use the Wiener filter, which is also known as $l^2$ ridge regulation 
($C=\norm{x}^2_2$), to find a regularized solution in Fourier space. \citet{HSC1-massMaps} apply the method of 
\citet{LSS-massMap-Wiener-Simon2009} to the first year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}. 
However, the density maps reconstructed by this method suffer from a smearing along the line-of-sight direction with 
a standard deviation of $\sigma_z=0.2 \sim 0.3$.

\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version of $l^1$ lasso regulation ($C=\norm{x}^1_1$) 
to find a sparse solution in the Starlets dictionary space \citep{Starlet-Starck2015}. \citet{LSS-massMap-Glimpse3D-Leonard2014}
apply a greedy coordinate descent algorithm, which selects the steepest coordinate in each iteration, to find the minima 
of a non-convex loss function penalized with the firm thresholding function. \citet{LSS-massMap-Glimpse3D-Leonard2014} 
significantly reduce the smearing along the line-of-sight, however, the stability of the non-convex optimization and
greedy coordinate descent algorithm has not been fully justified. Moreover, the Starlets functions are not designed to 
model the profile of clumpy mass in the universe.

$N$-body simulations have shown that the dark matter is distributed in halos connected by filaments, and the density 
profile of a single halo follows the NFW function \citep{halo-NFW1997ApJ}.
We construct a dictionary with multi-scale NFW atoms.  The atoms follow multi-scale surface density profiles of NFW 
functions \citep{haloModel-TJ2003-3pt} on the transverse plane. We follow \citet{LSS-massMap-Glimpse3D-Leonard2014} 
to neglect the depth of halos since the resolution scale of the reconstruction in the line-of-sight direction is much 
larger than the scales of halos. Therefore, we set the profile of the NFW atoms in the line-of-sight as the Dirac delta 
function. The multi-scale NFW atoms are used to model the profiles of halos which is assumed to be sparsely distributed 
in the universe. With the sparsity prior, the adaptive lasso regularization \citep{AdaLASSO-Zou2006} is used to reconstruct 
the density field. We find that, in contrast to the standard lasso estimator which smears the structure along the line-of-sight,
the addaptive lasso is able to significantly reduce the smearing effect.

@@

This paper is organized as follows.
Section \ref{sec:Method} proposes the new method for $3$-D density map reconstruction.
Section \ref{sec:Test} Tests our algorithm on HSC-like simulations.
Section \ref{sec:Sum} summarizes and discusses the future development of the method.

@@

The lensing convergence map at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line-of-sight is
\begin{equation}
\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s}
\frac{\delta(\vec{\theta},\chi_l)}{a(\chi_l)},
\end{equation}
where $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the matter density parameter, $c$ is the speed
of light, and $a(\chi_l)$ is the scale parameter at the lens position.

@@

\begin{figure*}[!t]
\centering
\subfigure[lasso]{\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-lasso.pdf}}
\subfigure[adaptive lasso]{\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-alasso.pdf}}
\caption{The result of density map reconstruction with standard lasso (left) and adaptive lasso (right). The input density 
        map is from a NFW halo with mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso reconstruction 
        smear the density field along the line-of-sight direction (vertical direction in the plots). Noises on shear measurements 
        are neglected in this simulation.} \label{fig-lassoVsadaLasso}
\end{figure*}

@@

We propose to use multi-scale NFW atoms, denoted as $\{\phi_1,...,\phi_N\}$, as our dictionary basi.
On the transverse plane, the NFW atoms follow surface density profiles of NFW halos
\citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and truncation radius $c \theta_\alpha$ ,
where $c$ is the concentration of NFW halos.
As the scales of halos are much less than the reachable redshift resolution, we neglect the depth of halo on the
line-of-sight direction and set the profiles of NFW atoms in the line-of-sight direction to $1$-D Dirac delta 
functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}. 
The multi-scale NFW atoms are defined as
\begin{equation}
\begin{split}
\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 } F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
&  (s=1..N)
\end{split}
\end{equation}
where
\begin{equation}
F(x)=
\begin{cases}
-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccosh \left(\frac{x^2+c}{x(1+c)}\right)}{(1-x^2)^{3/2}}  & (x<1),\\
\frac{\sqrt{c^2-1}}{3(1+c)} (1+\frac{1}{c+1}) & (x=1),\\
-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccos\left(\frac{x^2+c}{x(1+c)}\right)}{(x^2-1)^{3/2}} & (1<x\leq c),\\
0& (x>c).
\end{cases}
\end{equation}
$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for NFW atoms in different scale frames.

@@

$W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line-of-sight component
$W_\times(z)$
\begin{equation}
W(\vec{\theta},z)=W_T(\vec{\theta}) W_\times (z).
\end{equation}
In this paper, we use an isotropic $2$-D Gaussian kernel and a $1$-D top-hat kernel to smooth the measurements in the 
transverse plane and the line-of-sight direction, the smoothing kernel is 
\begin{equation}
\begin{split}
W_T(\vec{\theta}) &=\frac{1}{2\pi\beta^2}\exp(-\frac{|\vec{\theta}|}{2\beta^2}),\\
W_\times (z) &=
\begin{cases}
1/\Delta z& (|z|<\Delta z/2),\\
0& else.
\end{cases}
\end{split}
\end{equation}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
 \caption{The left panel shows the stacked distribution of deviations of detected peak positions 
 from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane and the 
 $y$-axis is for the deviation of the redshift. The peaks inside the dashed black box are regarded as true detections. The 
 right panel focus on the deviation of detected peaks in the line-of-sight direction. The $x$-axis shows the input redshifts 
 and the $y$-axis is the redshift of the detected peak. The cross symbols show the average redshift of detected peak for 
 halos with different input redshift and mass and the error-bars are the scatter of the corresponding peak redshifts. All 
 of the results in this figure are based on the NFW atoms.}
\end{figure*}

We pixelize the smoothed shear field into a $N_\theta \times N_\theta \times N_s$ grid, where $N_\theta$
is the number of pixels of two orthogonal axes of the transverse plane and $N_s$ is the number of pixels of the
line-of-sight axis. $\gamma_{\alpha}$ is used to denote the value recorded on pixel with index $\alpha$, where $\alpha=
1...N_\theta \times N_\theta \times N_s$. The grids on the transverse plans are equally spaced, therefore fast Fourier
transform (FFT) can be used to boost the speed of linear operation on the transverse plan, whereas the grids in the 
line-of-sight direction follow equal number binning as shown in Figure \ref{fig-bestpz}.

Similarly, we pixelize each scale frame of the parameter $x$ into a $N_\theta \times N_\theta \times N_l$ grid. 
The pixelization of the parameter field $x$ on the transverse plan for each scale frame is exactly the same as the 
pixelization of the smoothed shear field on the transverse plane. Whereas the parameter field is pixelized into equal 
spaced grids in the line-of-sight direction. Here, we use $N_l$ to denote the number of the lens planes and $x_{\beta}$ to 
denote the element of the parameter with index $\beta$, where $\beta=1...N_\theta \times N_\theta \times N_l \times N$. 
The corresponding pixelized elements of the forward transform matrix $\mathbf{A}$ is denoted as $A_{\alpha\beta}$.

@@

The lasso algorithm selects the parameters which are relevant to the measurements and simultaneously estimate the value of 
the selected parameters. However, it has been shown by 
\citet{AdaLASSO-Zou2006} that when the column vectors of the projection matrix $\mathbf{A'}$ are highly correlated, 
lasso cannot select the relevant parameters from the parameter space consistently. Moreover, the estimated parameters 
are biased due to the shrinkage process in the lasso regression. We note that, for the density map reconstruction problem, 
the effective basis vectors are highly correlated since, as shown in Figure \ref{fig-corlensKer}, the lensing kernels for 
lenses at different redshifts are highly correlated. Therefore, the lasso algorithm cannot select the consistent mass in  
the line-of-sight direction and the reconstructed mass sufferes from smears in the line-of-sight direction even in the 
absence of noise on shear measurements. 
Figure \ref{fig-lassoVsadaLasso} shows the reconstructions of the mass map of a single halo with halo mass equals 
$M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The noises on shear measurements are not included. The left panel of 
Figure \ref{fig-lassoVsadaLasso} is the reconstruction with lasso algorithm which shows a significant smear along the line-of-sight.

@@

In this section, we simulate weak lensing shear fields induced by a group of halos with various halo masses 
and redshifts. The shear distortion fields are applied to HSC mock catalogs with different realizations of HSC-like shape 
noises and photo-$z$ uncertainties (Section \ref{subsec:Sims}).

@@

We sample halos in two dimensional redshift-mass plane. The redshift-mass plane is evenly divided into eight redshift bins
and eight mass bins. The input redshifts and masses are shifted by random values for each halo from the centers 
of the bins.
The concentration of the NFW halo is a function of the halo's mass and redshift according to 
\citet{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}
The weak lensing shear fields of these NFW halos are simulated according to \citet{haloModel-TJ2003-3pt}. The shear 
distortions are applied to galaxy catalogs with HSC-like shape noise and photo-$z$ uncertainty.

@@

We develope a novel method to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
Our method models $3$-D density contrast maps as a summation of NFW atoms with multiple comoving radius and point mass atoms
in the $3$-D space binned with photometric redshift. The NFW atoms are used to model the mass in isolated halos and the 
point mass atoms are used to model the structures close to the resolution limit of the reconstruction.

>>>>

\begin{document}
\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction:
Reducing the line of sight smearing.}
%\author{Xiangchong Li}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Masamune Oguri}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
%\author{Wentao Luo}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{HSC Collaboration}
%\noaffiliation
%\email{xiangchong.li@ipmu.jp}

\begin{abstract}
A new method is developed to reconstruct $3$-D density contrast maps from photometric weak-lensing shear measurements.
The $3$-D density contrast maps are modeled as a summation of the NFW basis atoms which have $2$-D multi-scale NFW surface
density profiles on the transverse plane and $1$-D Dirac delta functions in the line of sight direction. With the prior
assumption that the density fields can be sparsely represented by the NFW basis atoms, it is reconstructed using an
oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using the HSC-like shape noise and
photo-$z$ uncertainty.
Our findings are summarized as folllows: 1) The global minima solution of the standard lasso algorithm suffers from a
smear of structure in the line of sight direction even in the absence of shape nosie.
2) The global minima solution of addaptive lasso algorithm significantly removes the line of sight smear of structure.
\end{abstract}

@@

Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line of sight
due to the influence of gravity. As a result of the light distortion, the shapes of the background galaxies are coherently
distorted. Such effect, which is known as weak-lensing, imprints the information of foreground mass density distribution
to the background galaxy images and offers a direct probe into the mass density distribution in our universe
\citep[see][for recent reviews]{revKilbinger15,revRachel17}.

@@

Several large scale surveys target to study the weak-lensing effect at high precision level (e.g. HSC \citep{HSC1-data}, KIDS
\citep{KIDS13}, DES \citep{DES05}, LSST \citep{LSSTScienceBook}, Euclid \citep{Euclid2011}, WFIRST \citep{WFIRST15}).

The primary goal of most weak-lensing surveys is to constrain the cosmology model through $2$-point correlations. The studies
include galaxy-galaxy lensing which cross correlating the shear field ($\gamma$) with the positions of foreground galaxies
\citep{gglens-GAMA-Han2014,gglens-BossCFHTMore2015,gglens-DES1},
and cosmic shear which auto-correlates the shear measurements
\citep{cosmicShearRealKids450,cosmicShear-DES1,cosmicShear_HSC1_Chiaki2019,cosmicShear_HSC1_Hamana2019}.
Since shear is directly related to the matter distribution as shown in eq. (\ref{eq-intro-delta2shear}), Galaxy-galaxy lensing
probes into the correlation between the matter field and galaxy field, on the other hand, cosmic shear probes into the
auto-correlation of matter field.

The reconstruction of density map from shear measurements also receive considerable interest as it reaches the nonlinear scales.
$2$-D density map reconstruction which recover an integration of projected mass along the line of sight has been well studied
within the community \citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016,sparseBaysianMassMap-Price2020}
and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However, the
reconstruction of $3$-D mass map is still a challenging task.

@@

\citet{LSS-massMap-Wiener-Simon2009} propose to use the Wiener filter, which is also known as $l^2$ ridge regulation
($C=\norm{x}^2_2$), to find a regularized solution in Fourier space. \citet{HSC1-massMaps} apply the method of
\citet{LSS-massMap-Wiener-Simon2009} to the first-year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}.
However, the density maps reconstructed by this method suffer from a smearing along the line of sight direction with
a standard deviation of $\sigma_z=0.2 \sim 0.3$.

\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version of $l^1$ lasso regulation ($C=\norm{x}^1_1$)
to find a sparse solution in the Starlets dictionary space \citep{Starlet-Starck2015}. \citet{LSS-massMap-Glimpse3D-Leonard2014}
apply a greedy coordinate descent algorithm, which selects the steepest coordinate in each iteration, to find the minima
of a non-convex loss function penalized with the firm thresholding function. \citet{LSS-massMap-Glimpse3D-Leonard2014}
significantly reduce the smearing along the line of sight, however, the stability of the non-convex optimization and
greedy coordinate descent algorithm has not been fully justified. Moreover, the Starlets functions are not designed to
model the profile of clumpy mass in the universe.

$N$-body simulations have shown that the dark matter is distributed in halos connected by filaments, and the density
profile of a single halo follows the NFW function \citep{halo-NFW1997ApJ}.
We construct a dictionary with multi-scale NFW atoms.  The atoms follow multi-scale surface density profiles of NFW
functions \citep{haloModel-TJ2003-3pt} on the transverse plane. We follow \citet{LSS-massMap-Glimpse3D-Leonard2014}
to neglect the depth of halos since the resolution scale of the reconstruction in the line of sight direction is much
larger than the scales of halos. Therefore, we set the profile of the NFW atoms in the line of sight as the Dirac delta
function. The multi-scale NFW atoms are used to model the profiles of halos which is assumed to be sparsely distributed
in the universe. With the sparsity prior, the adaptive lasso regularization \citep{AdaLASSO-Zou2006} is used to reconstruct
the density field. We find that, in contrast to the standard lasso estimator which smears the structure along the line of sight,
the addaptive lasso is able to significantly reduce the smearing effect.

@@

This paper is organized as follows.
In Section \ref{sec:Method}, we propose the new method for $3$-D density map reconstruction.
In Section \ref{sec:Test}, we test the novel algorithm on HSC-like simulations.
In Section \ref{sec:Sum}, we summarize and discuss the future development of the method.

@@

The lensing convergence map at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line of sight is
\begin{equation}
\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s}
\frac{\delta(\vec{\theta},\chi_l)}{a(\chi_l)},
\end{equation}
where $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the matter density parameter, $c$ is the speed
of light, and $a(\chi_l)$ is the scale parameter at the lens position.

@@

\begin{figure*}[!t]
\centering
\subfigure[lasso]{\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-lasso.pdf}}
\subfigure[adaptive lasso]{\includegraphics[width=0.49\textwidth]{delta-3-7-pz-nn-alasso.pdf}}
\caption{The result of density map reconstruction with standard lasso (left) and adaptive lasso (right). The input density
        map is from a NFW halo with mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso reconstruction
        smear the density field along the line of sight direction (vertical direction in the plots). Noises on shear measurements
        are neglected in this simulation.} \label{fig-lassoVsadaLasso}
\end{figure*}

@@

We propose to use multi-scale NFW atoms, denoted as $\{\phi_1,...,\phi_N\}$, as our dictionary basi.
On the transverse plane, the NFW atoms follow surface density profiles of NFW halos
\citep{haloModel-TJ2003-3pt} with scale radius $\theta_\alpha$ and truncation radius $c \theta_\alpha$ ,
where $c$ is the concentration of NFW halos.
As the scales of halos are much less than the reachable redshift resolution, we neglect the depth of halo on the
line of sight direction and set the profiles of NFW atoms in the line of sight direction to $1$-D Dirac delta
functions as suggested by \citep{LSS-massMap-Glimpse3D-Leonard2014}.
The multi-scale NFW atoms are defined as
\begin{equation}
\begin{split}
\phi_\alpha(\vec{r}) =&\frac{f }{2 \pi \theta_\alpha^2 } F(|\vec{\theta}|/\theta_\alpha) \delta_D(z),\\
&  (s=1..N)
\end{split}
\end{equation}
where
\begin{equation}
F(x)=
\begin{cases}
-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccosh \left(\frac{x^2+c}{x(1+c)}\right)}{(1-x^2)^{3/2}}  & (x<1),\\
\frac{\sqrt{c^2-1}}{3(1+c)} (1+\frac{1}{c+1}) & (x=1),\\
-\frac{\sqrt{c^2-x^2}}{(1-x^2)(1+c)} + \frac{\arccos\left(\frac{x^2+c}{x(1+c)}\right)}{(x^2-1)^{3/2}} & (1<x\leq c),\\
0& (x>c).
\end{cases}
\end{equation}
$f=1/[\ln (1+c)-c/(1+c)]$. In this work, we fix $c=4$ for NFW atoms in different scale frames.

@@

$W(\vec{\theta},z)$ can be decomposed into a transverse component $W_T(\vec{\theta})$ and a line of sight component
$W_\times(z)$
\begin{equation}
W(\vec{\theta},z)=W_T(\vec{\theta}) W_\times (z).
\end{equation}
In this paper, we use an isotropic $2$-D Gaussian kernel and a $1$-D top-hat kernel to smooth the measurements in the
transverse plane and the line of sight direction, the smoothing kernel is
\begin{equation}
\begin{split}
W_T(\vec{\theta}) &=\frac{1}{2\pi\beta^2}\exp(-\frac{|\vec{\theta}|}{2\beta^2}),\\
W_\times (z) &=
\begin{cases}
1/\Delta z& (|z|<\Delta z/2),\\
0& else.
\end{cases}
\end{split}
\end{equation}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
 \caption{The left panel shows the stacked distribution of deviations of detected peak positions
 from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane and the
 $y$-axis is for the deviation of the redshift. The peaks inside the dashed black box are regarded as true detections. The
 right panel focus on the deviation of detected peaks in the line of sight direction. The $x$-axis shows the input redshifts
 and the $y$-axis is the redshift of the detected peak. The cross symbols show the average redshift of detected peak for
 halos with different input redshift and mass and the error-bars are the scatter of the corresponding peak redshifts. All
 of the results in this figure are based on the NFW atoms.}
\end{figure*}

We pixelize the smoothed shear field into a $N_\theta \times N_\theta \times N_s$ grid, where $N_\theta$
is the number of pixels of two orthogonal axes of the transverse plane and $N_s$ is the number of pixels of the
line of sight axis. $\gamma_{\alpha}$ is used to denote the value recorded on pixel with index $\alpha$, where $\alpha=
1...N_\theta \times N_\theta \times N_s$. The grids on the transverse plans are equally spaced, therefore fast Fourier
transform (FFT) can be used to boost the speed of linear operation on the transverse plan, whereas the grids in the
line of sight direction follow equal number binning as shown in Figure \ref{fig-bestpz}.

Similarly, we pixelize each scale frame of the parameter $x$ into a $N_\theta \times N_\theta \times N_l$ grid.
The pixelization of the parameter field $x$ on the transverse plan for each scale frame is exactly the same as the
pixelization of the smoothed shear field on the transverse plane. Whereas the parameter field is pixelized into equal
spaced grids in the line of sight direction. Here, we use $N_l$ to denote the number of the lens planes and $x_{\beta}$ to
denote the element of the parameter with index $\beta$, where $\beta=1...N_\theta \times N_\theta \times N_l \times N$.
The corresponding pixelized elements of the forward transform matrix $\mathbf{A}$ is denoted as $A_{\alpha\beta}$.

@@

The lasso algorithm selects the parameters which are relevant to the measurements and simultaneously estimate the value of
the selected parameters. However, it has been shown by
\citet{AdaLASSO-Zou2006} that when the column vectors of the projection matrix $\mathbf{A'}$ are highly correlated,
lasso cannot select the relevant parameters from the parameter space consistently. Moreover, the estimated parameters
are biased due to the shrinkage process in the lasso regression. We note that, for the density map reconstruction problem,
the effective basis vectors are highly correlated since, as shown in Figure \ref{fig-corlensKer}, the lensing kernels for
lenses at different redshifts are highly correlated. Therefore, the lasso algorithm cannot select the consistent mass in
the line of sight direction and the reconstructed mass sufferes from smears in the line of sight direction even in the
absence of noise on shear measurements.
Figure \ref{fig-lassoVsadaLasso} shows the reconstructions of the mass map of a single halo with halo mass equals
$M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The noises on shear measurements are not included. The left panel of
Figure \ref{fig-lassoVsadaLasso} is the reconstruction with lasso algorithm which shows a significant smear along the line of sight.

@@

In this section, we simulate weak-lensing shear fields induced by a group of halos with various halo masses
and redshifts. The shear distortion fields are applied to HSC mock catalogs with different realizations of HSC-like shape
noises and photo-$z$ uncertainties (Section \ref{subsec:Sims}).

@@

We sample halos in two dimensional redshift-mass plane. The redshift-mass plane is evenly divided into eight redshift bins
and eight mass bins. The input redshifts and masses are shifted by random values for each halo from the centers
of the bins.
The concentration of the NFW halo is a function of the halo's mass and redshift according to
\citet{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}
The weak-lensing shear fields of these NFW halos are simulated according to \citet{haloModel-TJ2003-3pt}. The shear
distortions are applied to galaxy catalogs with HSC-like shape noise and photo-$z$ uncertainty.

@@

We develope a novel method to reconstruct $3$-D density contrast maps from photometric weak-lensing shear measurements.
Our method models $3$-D density contrast maps as a summation of NFW atoms with multiple comoving radius and point mass atoms
in the $3$-D space binned with photometric redshift. The NFW atoms are used to model the mass in isolated halos and the
point mass atoms are used to model the structures close to the resolution limit of the reconstruction.
